Attempting to write a full model

### 2016-09-14 R/misc/fullModel.rmd
finished moving to c++

            list(c(dS, dI, dSS, dSI, dII), 
            		 ##tot_I = tot_I, mean_V = tot_V/tot_I
            		 inf.SI.to2)
        })
    }
}

@@

microbenchmark(
tmpa = c(unname(g2(0, unlist(yini4), expand(HIVpars.mean))$dI)),
tmpb = c(unname(model2(expand(HIVpars.mean), infection = TRUE, mortality = TRUE)(0, unlist(yini4), expand(HIVpars.mean))[[1]][4:66]))
)
##1:3, 4:66. 67:75, 76:264
##-c(1:264)
all.equal(tmpa, tmpb)
plot(tmpa)
plot(tmpb)
```

InfSIto

>>>>

            list(c(dS, dI, dSS, dSI, dII), 
            		 ##tot_I = tot_I, mean_V = tot_V/tot_I
            		 mort.SI.out)
        })
    }
}

@@

microbenchmark(
tmpa = c(unname(g2(0, unlist(yini4), expand(HIVpars.mean))$dSI)),
tmpb = c(unname(model2(expand(HIVpars.mean), infection = TRUE, mortality = TRUE)(0, unlist(yini4), expand(HIVpars.mean))[[1]][76:264]))
)
##1:3, 4:66. 67:75, 76:264
##-c(1:264)
all.equal(tmpa, tmpb)
plot(tmpa)
plot(tmpb)
```
